QPLIB: A Library of Quadratic Programming Instances

### 2018-08-23 methods.tex
Update methods.tex

Asymptotically complete methods do not usually require a starting point, and, if given sufficient time (infinite in the worst case) will identify a globally optimal solution with probability one. Most often, these methods are meta-heuristics, involving an element of random choice, which exploit a given (heuristic) local search procedure.

>>>>

\textcolor{green}{An asymptotically complete method reaches a global minimum with certainty or
at least with probability one if allowed to run indefinitely long, but has no means to know when a global minimizer has been found (see \cite{neumaier}).}
%
%Asymptotically complete methods do not usually require a starting point, and, if given sufficient time (infinite in the worst case) will identify a globally optimal solution with probability one. 
%
Most often, these methods are meta-heuristics, involving an element of random choice, which exploit a given (heuristic) local search procedure.
